### 2016-06-17 capability-machine.tex
Finally add the nitpickings I promised.

``Continuation'' relation:
\begin{align*}
  \stdkr \quad : & \quad  \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stdkr(W) \defeq & \{ \npair{c} \mid \\
                   & \quad \forall v \in \stdvr(W)\ldotp \\
                   & \qquad  \forall W' \future W\ldotp %on the whiteboard, we had public future world.
                     \forall \heapSat{n'}{W'} \ldotp \forall \reg \in \stdrr(W') \\
                   & \qquad \quad (n,reg\update{r_0}{v}\update{\pcreg}{\updatePcPerm{c}}, \heap) \in \observations(W) \}
\end{align*}
\lau{$r_1$ contains the ``return value'', shouldn't that be the one we quantify over?} \\
\lau{When continuation is invoked, it has to be in registers, but here we do not require it to be in the value relation, so it seems impossible to show some of the required conditions.}
``Expression'' relation:
\begin{align*}
  \stder \quad : & \quad \Worlds \monfun \UPred{\Words} \\%TODO: Check whether this needs to be monotone
  \stder(W) \defeq & \{ \npair{\pc} \mid \\
                   & \quad \forall \reg \in \stdrr(W) \ldotp \\
                   & \qquad \forall \npair{c} \in \stdkr(W) \ldotp \\
                   & \qquad \quad  \forall \heapSat{n}{W}, \heap_f \ldotp \\
                   & \qquad \qquad (n,\reg\update{r_0}{c}\update{\pcreg}{\pc},\heap \uplus \heap_f) \in \observations(W) \}
\end{align*}

>>>>

``Continuation'' relation:
\begin{align*}
  \stdkr \quad : & \quad  \Worlds \monfun \UPred{\Words} \\%TODO: What should this be?
  \stdkr(W) \defeq & \{ \npair{c} \mid \\
                   & \quad \forall v \in \stdvr(W)\ldotp \\
                   & \qquad  \forall W' \future W\ldotp %on the whiteboard, we had public future world.
                     \forall \heapSat{n'}{W'} \ldotp \forall \reg \in \stdrr(W') \\
                   & \qquad \quad (n,reg\update{r_0}{v}\update{\pcreg}{\updatePcPerm{c}}, \heap) \in \observations(W) \}
\end{align*}
\lau{$r_1$ contains the ``return value'', shouldn't that be the one we quantify over?} \\
\lau{When continuation is invoked, it has to be in registers, but here we do not require it to be in the value relation, so it seems impossible to show some of the required conditions.}
\dominique{$n'$ is unbound in the definition of $\stdkr$. }
\dominique{$v \in \stdvr(W)$ should be $v \in \stdvr(W')$ in the definition of $\stdkr$? }
\dominique{$\observations(W)$ should be $\observations(W')$ in the definition of $\stdkr$? }
``Expression'' relation:
\begin{align*}
  \stder \quad : & \quad \Worlds \monfun \UPred{\Words} \\%TODO: Check whether this needs to be monotone
  \stder(W) \defeq & \{ \npair{\pc} \mid \\
                   & \quad \forall \reg \in \stdrr(W) \ldotp \\
                   & \qquad \forall \npair{c} \in \stdkr(W) \ldotp \\
                   & \qquad \quad  \forall \heapSat{n}{W}, \heap_f \ldotp \\
                   & \qquad \qquad (n,\reg\update{r_0}{c}\update{\pcreg}{\pc},\heap \uplus \heap_f) \in \observations(W) \}
\end{align*}
